### 2011-11-23 doc/theses/vitasek/chapter-0-preface.tex
Thesis: finished?

Pseudocode examples such as the one in Listing \ref{listing-example} will always be presented in a functional way, with inputs and outputs of the function clearly marked in~the~beginning.

>>>>

Pseudocode examples such as the one in Listing \ref{listing-example} will always be presented in a functional way, with inputs and outputs of the function clearly marked at~the~beginning.

### 2011-11-23 doc/theses/vitasek/chapter-1-definitions.tex
Thesis: finished?

We shall use the representation introduced in \cite{fidax}, where an XML file is~represented by a labeled tree consisting of nodes for elements, attributes and simple text data. Parent nodes are connected to child nodes with edges. This tree shall be called an \textit{XML tree}. For a given node $v$ of an XML tree we define $label(v)$ (name of the node in in the document, only for elements and attributes), $id(v)$ (unique identifier across the document) and $value(v)$ (text content, only for attributes and simple text data) in the same way as the cited article does.

@@

This example introduces an XML file fragment that will be used for demonstration throughout this work. An XML tree representing it is in Figure \ref{image-definitions-example-xml-tree}(a), where each node is annotated with a triplet $label(v) : id(v) : value(v)$.

@@

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree} 
  \centering
    \subfigure[XML tree]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree}}
    \subfigure[Attribute Mappings]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree-ams}}
\end{figure}

@@

An \texttt{ID} attribute \textsc{must} have a declared default of \texttt{\#IMPLIED}\footnote{\texttt{\#IMPLIED} means that the attribute has a specified default value.} or \texttt{\#REQUIRED}\footnote{\texttt{\#REQUIRED} means that the attribute cannot be empty.}.

@@

\begin{define}[ID set]
A set of candidate attribute mappings $I = \{m_1, \ldots m_n\}$ is an \textit{ID set} iff
\[\bigcap_{m_i \in I} \tau(m_i) = \emptyset \wedge \bigcap_{m_i \in I} \iota(m_i) = \emptyset.\]
\end{define}

@@

This definition of weight for AMs or AM sets comes from \cite{fidax} again. Let $M = \{m_1, \dots m_i\}$ be the set of all non-empty AMs in the document.

@@

\paragraph{Example}
Coverage of $M_{y}^{a}$ in our example is $(0+0+1) / (2+1+1+1) = 0.2$. Coverage of $M_{z}^{a}$ is $0.2$ as well, all the other mappings have coverage $0$.
\\

@@

Note that this definition of weight is quite arbitrary and all the algorithms mentioned later could easily work with AM weight defined in any other way, even for example defined interactively by the user.

>>>>

We shall use the representation introduced in \cite{fidax}, where an XML file is~represented by a labeled tree consisting of nodes for elements, attributes and simple text data. Parent nodes are connected to child nodes with edges. This tree shall be called an \textit{XML tree}. For a given node $v$ of an XML tree we define $label(v)$ (name of the node in the document, only for elements and attributes), $id(v)$ (unique identifier across the document) and $value(v)$ (text content, only for attributes and simple text data) in the same way as the cited article does.

@@

This example introduces an XML file fragment that will be used for demonstration throughout the work. An XML tree representing it is in Figure \ref{image-definitions-example-xml-tree}(a), where each node is annotated with a triplet $label(v) : id(v) : value(v)$.

@@

\begin{figure}
  \caption{Example XML Tree}
  \label{image-definitions-example-xml-tree} 
  \centering
    \subfigure[XML Tree]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree}}
    \subfigure[Attribute Mappings]{\includegraphics[width=.45\textwidth]{images/definitions/xml-tree-ams}}
\end{figure}

@@

An \texttt{ID} attribute \textsc{must} have a declared default of \texttt{\#IMPLIED}\footnote{\texttt{\#IMPLIED} means that the attribute has a specified default value.} or \texttt{\#RE\-QUIRED}\footnote{\texttt{\#REQUIRED} means that the attribute cannot be empty.}.

@@

\begin{define}[ID set]
A set of candidate attribute mappings $I = \{m_1, \ldots m_n\}$ is an \textit{ID set} iff
\[\bigcap_{m_i \in I} \tau(m_i) = \emptyset\:\text{and} \bigcap_{m_i \in I} \iota(m_i) = \emptyset.\]
\end{define}

@@

This definition of weight for AMs or AM sets comes from \cite{fidax} again. We need the notions of \textit{support} and \textit{coverage} to define it. Let $M = \{m_1, \dots m_i\}$ be the set of all non-empty AMs in the document.

@@

\paragraph{Example}
Coverage of $M_{y}^{a}$ in our example is $(0+0+1) / (2+1+1+1) = 0.2$. Coverage of $M_{z}^{a}$ is $0.2$ as well; all the other mappings have coverage $0$.
\\

@@

Note that this definition of weight is quite arbitrary and all the algorithms mentioned later could easily work with AM weight defined in any other way, even, for example, defined interactively by the user.

### 2011-11-23 doc/theses/vitasek/diplomka.tex
two side printing margins
Thesis: merging Kesy, fixing singletons and duplex.
Thesis: fixing page numbers and a figure.
Thesis: merging Kesy.
Thesis: finished?

\documentclass[a4paper,12pt,twoside]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage[title,titletoc]{appendix}
%\usepackage{textgreek}
\usepackage{nomencl}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{complexity}
%\usepackage{refcheck}
\usepackage[pdfborder=0 0 0,pdftex,unicode]{hyperref}
\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

@@

\setlength{\hoffset}{-1in} %left margin will be 0, as hoffset is by default 1inch
\setlength{\voffset}{-1in} %analogous voffset
\setlength{\oddsidemargin}{4cm}
\setlength{\evensidemargin}{4cm}
\setlength{\topmargin}{25mm}
\setlength{\footskip}{1cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\setlength{\textheight}{23.7cm}
\setlength{\textwidth}{14.5cm}
\let\openright=\clearpage

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Ire\-na Mlýn\-ko\-vá, Ph.D.}
\def\mfplacedate{Praha, 2011}

@@

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Irena Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Mi\-chal Šva\-ger\-ka, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HV}.

@@

\openright
\pagestyle{plain}
\setcounter{page}{1}
\tableofcontents

% =============== TEXT ================
\newpage

@@

\newpage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%\nocite{*}
%\bibliographystyle{alpha}
%\bibliography{literature}
	\include{bibliography}

@@

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Algorithms}
\listofalgorithms

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\clearpage
\phantomsection
\addcontentsline{toc}{section}{List of Abbreviations}
\label{chapter-list-abbreviations}
\printnomenclature[2cm]

\openright
\clearpage
\phantomsection
\addappheadtotoc
\renewcommand{\appendixname}{Appendix}

>>>>

\documentclass[a4paper,12pt,twoside,openright]{report}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tgpagella}
\usepackage{xstring}
\usepackage{wrapfig}
\usepackage[title,titletoc]{appendix}
%\usepackage{textgreek}
\usepackage{nomencl}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{complexity}
%\usepackage{refcheck}
\usepackage[pdfborder=0 0 0,pdftex,unicode]{hyperref}
\DeclareFontShape{OT1}{cmtt}{bx}{n}{<5><6><7><8><9><10><10.95><12><14.4><17.28><20.74><24.88>cmttb10}{}

@@

\setlength{\hoffset}{-1in} %left margin will be 0, as hoffset is by default 1inch
\setlength{\voffset}{-1in} %analogous voffset
\setlength{\oddsidemargin}{4cm}
\setlength{\evensidemargin}{2.5cm}
\setlength{\topmargin}{25mm}
\setlength{\footskip}{1cm}
\setlength{\headheight}{0cm}
\setlength{\headsep}{0cm}
\setlength{\marginparwidth}{0cm}
\setlength{\marginparpush}{0cm}
\setlength{\textheight}{23.7cm}
\setlength{\textwidth}{14.5cm}
\let\openright=\clearpage

\def\mfauthor{Matej Vitásek}
\def\mfadvisor{RNDr. Ire\-na Mlýn\-ko\-vá, Ph.D.}
\def\mfplacedate{Prague 2011}

@@

\cleardoublepage

\noindent
I would like to thank everyone participating in the jInfer project for creating a~solid foundation for this work, namely Irena Mlýn\-ko\-vá, Mi\-chal Klem\-pa, Má\-rio Mi\-ku\-la, Ro\-bert Sme\-ta\-na and Mi\-chal Švi\-rec. The thanks goes again to Irena Mlýn\-ko\-vá for supervising this work, as well as everyone reviewing it, in no~particular order Lý\-dia Šva\-ger\-ko\-vá, Zu\-za\-na Ma\-sá\-ro\-vá, Mi\-chal Ke\-se\-ly and others\textsuperscript{HV}.

@@

\cleardoublepage
\pagestyle{plain}
\setcounter{page}{1}
\tableofcontents

% =============== TEXT ================

@@

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
%\nocite{*}
%\bibliographystyle{alpha}
%\bibliography{literature}
	\include{bibliography}

@@

\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{List of Algorithms}
\listofalgorithms

\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{List of Tables}
\listoftables

\cleardoublepage
\phantomsection
\addcontentsline{toc}{section}{List of Abbreviations}
\label{chapter-list-abbreviations}
\printnomenclature[2cm]

\openright
\cleardoublepage
\phantomsection
\addappheadtotoc
\renewcommand{\appendixname}{Appendix}
